---
title: "01_mice_info"
format: html
editor: visual
---

## JAXMice PARKINSON'S DISEASE MOUSE STRAIN SCRAPER


```{r}

## Output: data/JAX_Parkinson_Mouse_Strains.csv

library(chromote)
library(rvest)
library(dplyr)
library(purrr)
library(stringr)
library(tibble)
library(readr)
library(tidyr)

## 1. create folder ---------------
if (!dir.exists("data_raw")) dir.create("data_raw")


## 2. JAXMice Parkinson Disease url -------------------
jax_url <- paste0("https://mice.jax.org/?",
                  "linkBuilder=1",
                  "&stocktype=",
                  "&diseaseterm=",
                  "&straingroup=",
                  "&researcharea=Neurobiology%20Research",
                  "&researcharea2=Parkinson%27s%20Disease",
                  "&researcharea3=",
                  "&strainstatus=",
                  "&genesymbol=",
                  "&allelesymbol=",
                  "&geneticbackground=")
cat("JAX search URL:\n", jax_url, "\n\n")

## 3. Chrome scrapping -----------------
b <- ChromoteSession$new()
b$Page$navigate(jax_url)
cat("Loading JAX website...\n")
Sys.sleep(10)

## 4. functions for rendered HTML


get_html <- function(browser) {
  browser$Runtime$evaluate("document.documentElement.outerHTML")$result$value

}

## 5. scroll page to load dynamic content

for (i in 1:20) {
  b$Runtime$evaluate("window.scrollTo(0,
                     document.body.scrollHeight)")
  
  Sys.sleep(1)
}

## 6. reading page

html <- get_html(b)

page <- read_html(html)

page_text <- page %>%
  html_text2() %>%
  str_squish()

cat("\nFirst 1000 characters from page:\n\n",
  substr(page_text, 1, 5000),
  "\n\n")

## 7. extraction

nodes <- page %>%
  html_elements("a")

links <- tibble(text = nodes %>%
                  html_text2() %>%
                  str_squish(),
                url = nodes %>%
                  html_attr("href")) %>%
  filter(!is.na(url),
         url != "") %>%
  distinct()

cat("Total links detected:",
    nrow(links),
    "\n")

## 8. JAXMice strain link

mouse_links_raw <- links %>%
  filter(str_detect(paste(text, url),
                    regex("datasheet|strain|stock|jaxmice",
                          ignore_case = TRUE)))
cat("\nPotential mouse links:",
    nrow(mouse_links_raw),
    "\n\n")
print(mouse_links_raw,
      n = 250)
write_csv(mouse_links_raw,
          here::here("data_raw", 
                     "JAX_Parkinson_links_RAW.csv"))

## 9. standardized url

mouse_links <- mouse_links_raw %>%
  mutate(jax_url = case_when(str_starts(url, "https://") ~ url,
                             str_starts(url, "http://") ~ url,
                             str_starts(url, "//") ~ paste0("https:", url),
                             str_starts(url, "/") ~ paste0("https://mice.jax.org", url),
                             TRUE ~ paste0("https://mice.jax.org/", url))) %>%
  filter(!str_detect(jax_url,
                     regex("search|login|contact|cart",
                           ignore_case = TRUE))) %>%
  distinct(jax_url,
           .keep_all = TRUE)
cat("\nUnique potential strain pages:",
  nrow(mouse_links),
  "\n")
```

## The functions

```{r "functions"}
## 10. functions to extract text
extract_section <- function(text,
                            start_term,
                            end_terms,
                            max_chars = 2000) {
  
  if (is.na(text) || text == "") {return(NA_character_)}
  end_pattern <- paste(end_terms,
                       collapse = "|")
  pattern <- paste0(start_term,
                    "\\s*:?\\s*",
                    "(.{1,", max_chars, "}?)",
                    "(?=",
                    end_pattern,
                    "|$)" )
  result <- str_match(text,
                          regex(pattern,
                            ignore_case = TRUE,
                            dotall = TRUE))
  
  if (nrow(result) == 0 || is.na(result[1, 2])) return(NA_character_)
  result <- str_squish(result[1, 2])
  return(result)
}


## read and extract mouse text
extract_mouse <- function(url,
                          browser,
                          wait = 3) {
  cat("Reading:\n", url, "\n")
  tryCatch({
    ## to navigate
    browser$Page$navigate(url)
    Sys.sleep(wait)
    ## to scroll down
    browser$Runtime$evaluate("window.scrollTo(0, document.body.scrollHeight)")
    Sys.sleep(wait)
    ## rendered HTML
    html <- get_html(browser)
    page <- read_html(html)
    h1 <- page %>%
      html_element("h1")
    if (length(h1) > 0) {
      strain_name <- h1 %>%
        html_text2() %>%
        str_squish()
      } else {
      strain_name <- page %>%
        html_element("title") %>%
        html_text2() %>%
        str_squish()
    }
    full_text <- page %>%
      html_text2() %>%
      str_squish()
    stock_match <- str_extract(full_text,
                               regex("(Stock\\s*(No\\.?|Number)?|JR)\\s*[:#]?\\s*[0-9]{5,6}",
                                     ignore_case = TRUE))
    stock_number <- str_extract(stock_match,
                                "[0-9]{5,6}")
    
    common_uses <- extract_section(full_text,
                                   "Common Uses",
                                   c("Genetic Background",
                                     "Development",
                                     "Breeding",
                                     "Phenotype",
                                     "Availability",
                                     "Technical Support"), 1500)
    
    genetic_background <- extract_section(full_text,
                                          "Genetic Background",
                                          c("Common Uses",
                                            "Development",
                                            "Breeding",
                                            "Phenotype",
                                            "Availability",
                                            "Technical Support"), 1000)
    description <- extract_section(full_text,
                                   "Description",
                                   c("Development",
                                     "Phenotype",
                                     "Breeding",
                                     "Expression",
                                     "Molecular",
                                     "References"),
                                   3000)
    
    development <- extract_section(full_text,
                                   "Development",
                                   c("Phenotype",
                                     "Breeding",
                                     "Expression",
                                     "Molecular",
                                     "References",
                                     "Technical Support"),
                                   3000)
    
    phenotype <- extract_section(
      full_text,
      "Phenotype",
      c("Development",
        "Breeding",
        "Expression",
        "Molecular",
        "References",
        "Technical Support"),
      4000)
    
    breeding <- extract_section(
      full_text,
      "Breeding",
      c("Development",
        "Phenotype",
        "Expression",
        "Molecular",
        "References",
        "Technical Support"),
      2500)
    
    tibble(stock_number = stock_number,
           strain_name = strain_name,
           genetic_background = genetic_background,
           common_uses = common_uses,
           description = description,
           phenotype = phenotype,
           development = development,
           breeding = breeding,
           full_text = full_text,
           jax_url =url)
  }, 
  error = function(e) {
    message("ERROR: ",
            conditionMessage(e))
    
    tibble(stock_number = NA_character_,
           strain_name = NA_character_,
           genetic_background = NA_character_,
           common_uses = NA_character_,
           description = NA_character_,
           phenotype = NA_character_,
           development = NA_character_,
           breeding = NA_character_,
           full_text = NA_character_,
           jax_url = url)
  })
}
```



```{r}
## all mouse pages in the website
cat("\nBeginning extraction of individual mouse pages...\n")
mouse_data <- map_dfr(mouse_links$jax_url,
                      ~extract_mouse(url = .x,
                                     browser = b,
                                     wait = 3))
cat("\nMouse pages processed:",
    nrow(mouse_data), "\n")
mouse_data <- mouse_data %>%
  filter(!is.na(stock_number) |
    str_detect(full_text,
      regex("mouse|mice|strain|stock",
        ignore_case = TRUE)))
```



```{r}
pd_genes <- c("Gba1", "Snca",
              "Lrrk2",
              "Pink1", "Prkn", "Park7",
              "Vps35", "Uchl1",
              "Atp13a2", "Rab29", "Gak")
find_pd_genes <- function(x) {
  if (is.na(x)) {return(NA_character_)}
  found <- pd_genes[map_lgl(pd_genes,
                            ~str_detect(x,
                                        regex(paste0("\\b", .x, "\\b"),
                                              ignore_case = TRUE)))]
  if (length(found) == 0) {return(NA_character_)}
  paste(unique(found),
        collapse = "; ")
}

mouse_data <- mouse_data %>%
  mutate(gene = map_chr(full_text,
                        find_pd_genes))

## alpha synuclein related strains
mouse_data <- mouse_data %>%
  mutate(alpha_synuclein_related = case_when(str_detect(
    full_text,
    regex("alpha.?synuclein|α.?synuclein|Snca",
          ignore_case = TRUE)) ~ "YES",
    TRUE ~ "NO"))
```


## GD / GBA1 and PD model

```{r}
mouse_data <- mouse_data %>%
  mutate(gaucher_related = case_when(
      str_detect(full_text,
        regex(paste("Gba1",
            "GCase",
            "glucocerebrosidase",
            "glucosylceramide",
            "glucosylsphingosine",
            "Gaucher", sep = "|"),
          ignore_case = TRUE)) ~ "YES",
      TRUE ~ "NO"))

mouse_data <- mouse_data %>%
  mutate(pd_model_type = case_when(str_detect(full_text,
        regex("Gba1|GCase|glucocerebrosidase|Gaucher",
          ignore_case = TRUE)) ~
        "GBA1 / Gaucher-associated model",
      str_detect(full_text, regex("Snca|alpha.?synuclein|α.?synuclein",
          ignore_case = TRUE)) ~ "Alpha-synuclein model",
      str_detect(full_text,
        regex("Lrrk2",
          ignore_case = TRUE)) ~ "LRRK2 model",
      str_detect(full_text,
        regex("Pink1",
          ignore_case = TRUE)) ~ "PINK1 model",
      str_detect(full_text,
        regex("Prkn|Parkin",
          ignore_case = TRUE)) ~ "Parkin model",
      str_detect(full_text,
                 regex("Park7|DJ.?1",
          ignore_case = TRUE)) ~ "DJ-1 model",
      TRUE ~ "Other Parkinson-related model"))

mouse_data <- mouse_data %>%
  mutate(mouse_summary = paste0(if_else(!is.na(gene),
        paste0("Gene: ", gene, ". "), ""),
      if_else(!is.na(genetic_background),
        paste0("Background: ",
          genetic_background,
          ". "), ""),
      if_else(!is.na(common_uses),
        paste0("Common uses: ", common_uses, ". "), ""),
      if_else(!is.na(phenotype), paste0("Phenotype: ", phenotype), "")),
    mouse_summary = str_squish(mouse_summary))

View(mouse_data)

jax_parkinson_mice <- mouse_data %>%
  select(stock_number,
    strain_name,
    gene,
    pd_model_type,
    gaucher_related,
    alpha_synuclein_related,
    genetic_background,
    common_uses,
    description,
    phenotype,
    development,
    breeding,
    # jax_url,
    mouse_summary) %>%
  distinct(stock_number,
    # jax_url,
    .keep_all = TRUE) %>%
  arrange(desc(gaucher_related),
    gene,
    stock_number)
```


## Final results

```{r}
cat("FINAL NUMBER OF STRAINS:",
    nrow(jax_parkinson_mice),
    "\n")
print(jax_parkinson_mice %>%
        select(stock_number,
               strain_name,
               gene,
               pd_model_type,
               gaucher_related),
      n = Inf)
cat("\nPD model types:\n")
print(jax_parkinson_mice %>%
        count(pd_model_type,
              sort = TRUE))
cat("\nGaucher-related models:\n")
print(jax_parkinson_mice %>%
        filter(gaucher_related == "YES") %>%
        select(stock_number,
               strain_name,
               gene,
               pd_model_type))
write_csv(jax_parkinson_mice, 
          "data_raw/JAX_Parkinson_Mouse_Strains.csv",
          na = "")
write_csv(mouse_data, 
          "data_raw/JAX_Parkinson_Mouse_Strains_RAW.csv",
          na = "")
gaucher_pd_mice <- jax_parkinson_mice %>%
  filter(gaucher_related == "YES")
write_csv(gaucher_pd_mice,
          "data_raw/JAX_Gaucher_Parkinson_Mouse_Strains.csv",
          na = "")

b$close()
cat("\nFiles created:\n",
    "  data_raw/JAX_Parkinson_Mouse_Strains.csv\n",
    "  data_raw/JAX_Parkinson_Mouse_Strains_RAW.csv\n",
    "  data_raw/JAX_Gaucher_Parkinson_Mouse_Strains.csv\n")
```

# New codes


# JAX Parkinson's Disease Mouse Strains

This script extracts Parkinson's disease mouse strains and strain information
from the JAX Mice website.

```{r setup, message=FALSE, warning=FALSE}
library(chromote)
library(rvest)
library(dplyr)
library(purrr)
library(stringr)
library(tibble)
library(readr)
```

# 1. JAX Parkinson's Disease Website

```{r}
jax_url <- paste0(
  "https://mice.jax.org/?",
  "linkBuilder=1",
  "&stocktype=",
  "&diseaseterm=",
  "&straingroup=",
  "&researcharea=Neurobiology%20Research",
  "&researcharea2=Parkinson%27s%20Disease",
  "&researcharea3=",
  "&strainstatus=",
  "&genesymbol=",
  "&allelesymbol=",
  "&geneticbackground="
)

jax_url
```

# 2. Start Browser

```{r}
b <- ChromoteSession$new()
```

# 3. Function to Get Rendered HTML

```{r}
get_html <- function(browser) {
  
  html <- browser$Runtime$evaluate(
    "document.documentElement.outerHTML"
  )
  
  html$result$value
}
```

# 4. Open JAX Parkinson's Disease Page

```{r}
b$Page$navigate(jax_url)

Sys.sleep(5)
```

# 5. Scroll Through Search Results

```{r}
for (i in 1:15) {
  
  b$Runtime$evaluate(
    "window.scrollTo(0, document.body.scrollHeight)"
  )
  
  Sys.sleep(2)
}
```

# 6. Get Search Page HTML

```{r}
search_html <- get_html(b)

search_page <- read_html(search_html)

search_text <- search_page %>%
  html_text2() %>%
  str_squish()

substr(
  search_text,
  1,
  2000
)
```

# 7. Extract All Links

```{r}
all_links <- search_page %>%
  html_elements("a") %>%
  html_attr("href") %>%
  na.omit() %>%
  unique()

length(all_links)

head(
  all_links,
  30
)
```

# 8. Identify Mouse Strain Links

```{r}
strain_links <- all_links[
  str_detect(
    all_links,
    regex(
      "/strain/",
      ignore_case = TRUE
    )
  )
]

strain_links <- unique(
  strain_links
)

length(strain_links)

strain_links
```

# 9. Create Complete JAX URLs

```{r}
strain_links <- ifelse(
  str_detect(
    strain_links,
    "^https?://"
  ),
  strain_links,
  paste0(
    "https://mice.jax.org",
    strain_links
  )
)

strain_links <- unique(
  strain_links
)


mouse_links <- tibble(
  jax_url = strain_links
)


cat(
  "\nMouse strain links found:",
  nrow(mouse_links),
  "\n"
)

mouse_links
```

# 10. Function to Extract Text Sections

```{r}
extract_section <- function(text,
                            start_term,
                            end_terms,
                            max_chars = 2000) {
  
  if (is.na(text) ||
      text == "") {
    
    return(
      NA_character_
    )
  }
  
  
  end_pattern <- paste(
    end_terms,
    collapse = "|"
  )
  
  
  pattern <- paste0(
    start_term,
    "\\s*:?\\s*",
    "(.{1,", max_chars, "}?)",
    "(?=",
    end_pattern,
    "|$)"
  )
  
  
  result <- str_match(
    text,
    regex(
      pattern,
      ignore_case = TRUE,
      dotall = TRUE
    )
  )
  
  
  if (nrow(result) == 0 ||
      is.na(result[1, 2])) {
    
    return(
      NA_character_
    )
  }
  
  
  result <- str_squish(
    result[1, 2]
  )
  
  
  return(
    result
  )
}
```

# 11. Function to Extract Individual Mouse Page

```{r}
extract_mouse <- function(url,
                          browser,
                          wait = 3) {
  
  cat(
    "Reading:\n",
    url,
    "\n"
  )
  
  
  tryCatch({
    
    
    ## navigate to page
    
    browser$Page$navigate(
      url
    )
    
    Sys.sleep(
      wait
    )
    
    
    ## scroll down
    
    browser$Runtime$evaluate(
      "window.scrollTo(0, document.body.scrollHeight)"
    )
    
    Sys.sleep(
      wait
    )
    
    
    ## rendered HTML
    
    html <- get_html(
      browser
    )
    
    page <- read_html(
      html
    )
    
    
    ## strain name
    
    h1 <- page %>%
      html_element("h1")
    
    
    if (length(h1) > 0 &&
        !is.na(html_text2(h1))) {
      
      strain_name <- h1 %>%
        html_text2() %>%
        str_squish()
      
    } else {
      
      strain_name <- page %>%
        html_element("title") %>%
        html_text2() %>%
        str_squish()
    }
    
    
    ## complete page text
    
    full_text <- page %>%
      html_text2() %>%
      str_squish()
    
    
    ## JAX stock number
    
    stock_match <- str_extract(
      full_text,
      regex(
        paste0(
          "(Stock\\s*(No\\.?|Number)?|JR)",
          "\\s*[:#]?\\s*",
          "[0-9]{5,6}"
        ),
        ignore_case = TRUE
      )
    )
    
    
    stock_number <- str_extract(
      stock_match,
      "[0-9]{5,6}"
    )
    
    
    ## common uses
    
    common_uses <- extract_section(
      full_text,
      "Common Uses",
      c(
        "Genetic Background",
        "Description",
        "Development",
        "Phenotype",
        "Breeding",
        "Availability",
        "Technical Support"
      ),
      2000
    )
    
    
    ## genetic background
    
    genetic_background <- extract_section(
      full_text,
      "Genetic Background",
      c(
        "Common Uses",
        "Description",
        "Development",
        "Phenotype",
        "Breeding",
        "Availability",
        "Technical Support"
      ),
      1500
    )
    
    
    ## description
    
    description <- extract_section(
      full_text,
      "Description",
      c(
        "Development",
        "Phenotype",
        "Breeding",
        "Expression",
        "Molecular",
        "References",
        "Technical Support"
      ),
      4000
    )
    
    
    ## development
    
    development <- extract_section(
      full_text,
      "Development",
      c(
        "Phenotype",
        "Breeding",
        "Expression",
        "Molecular",
        "References",
        "Technical Support"
      ),
      4000
    )
    
    
    ## phenotype
    
    phenotype <- extract_section(
      full_text,
      "Phenotype",
      c(
        "Development",
        "Breeding",
        "Expression",
        "Molecular",
        "References",
        "Technical Support"
      ),
      5000
    )
    
    
    ## breeding
    
    breeding <- extract_section(
      full_text,
      "Breeding",
      c(
        "Development",
        "Phenotype",
        "Expression",
        "Molecular",
        "References",
        "Technical Support"
      ),
      3000
    )
    
    
    ## return data
    
    tibble(
      stock_number = stock_number,
      strain_name = strain_name,
      genetic_background = genetic_background,
      common_uses = common_uses,
      description = description,
      phenotype = phenotype,
      development = development,
      breeding = breeding,
      full_text = full_text,
      jax_url = url
    )
    
    
  },
  
  
  error = function(e) {
    
    message(
      "ERROR: ",
      conditionMessage(e)
    )
    
    
    tibble(
      stock_number = NA_character_,
      strain_name = NA_character_,
      genetic_background = NA_character_,
      common_uses = NA_character_,
      description = NA_character_,
      phenotype = NA_character_,
      development = NA_character_,
      breeding = NA_character_,
      full_text = NA_character_,
      jax_url = url
    )
    
  })
}
```

# 12. Extract All Mouse Strain Pages

```{r}
cat(
  "\nBeginning extraction of individual mouse pages...\n"
)


mouse_data <- map_dfr(
  mouse_links$jax_url,
  ~extract_mouse(
    url = .x,
    browser = b,
    wait = 3
  )
)


cat(
  "\nMouse pages processed:",
  nrow(mouse_data),
  "\n"
)
```

# 13. Clean Mouse Data

```{r}
mouse_data <- mouse_data %>%
  filter(
    !is.na(stock_number) |
      str_detect(
        full_text,
        regex(
          "mouse|mice|strain|stock",
          ignore_case = TRUE
        )
      )
  ) %>%
  distinct(
    jax_url,
    .keep_all = TRUE
  )


cat(
  "\nMouse strains retained:",
  nrow(mouse_data),
  "\n"
)
```

# 14. Identify Parkinson's Disease Genes

```{r}
pd_genes <- c(
  "Gba1",
  "Snca",
  "Lrrk2",
  "Pink1",
  "Prkn",
  "Park7",
  "Vps35",
  "Uchl1",
  "Atp13a2",
  "Rab29",
  "Gak",
  "Synj1",
  "Dnajc6",
  "Fbxo7"
)
```

```{r}
find_pd_genes <- function(x) {
  
  if (is.na(x)) {
    
    return(
      NA_character_
    )
  }
  
  
  found <- pd_genes[
    map_lgl(
      pd_genes,
      ~str_detect(
        x,
        regex(
          paste0(
            "\\b",
            .x,
            "\\b"
          ),
          ignore_case = TRUE
        )
      )
    )
  ]
  
  
  if (length(found) == 0) {
    
    return(
      NA_character_
    )
  }
  
  
  paste(
    unique(found),
    collapse = "; "
  )
}
```

```{r}
mouse_data <- mouse_data %>%
  mutate(
    gene = map_chr(
      full_text,
      find_pd_genes
    )
  )
```

# 15. Identify Important PD Mutations

```{r}
pd_mutations <- c(
  "A53T",
  "A30P",
  "E46K",
  "G2019S",
  "R1441C",
  "R1441G",
  "R1441H",
  "D409V",
  "L444P",
  "N370S"
)
```

```{r}
find_pd_mutations <- function(x) {
  
  if (is.na(x)) {
    
    return(
      NA_character_
    )
  }
  
  
  found <- pd_mutations[
    map_lgl(
      pd_mutations,
      ~str_detect(
        x,
        regex(
          paste0(
            "\\b",
            .x,
            "\\b"
          ),
          ignore_case = TRUE
        )
      )
    )
  ]
  
  
  if (length(found) == 0) {
    
    return(
      NA_character_
    )
  }
  
  
  paste(
    unique(found),
    collapse = "; "
  )
}
```

```{r}
mouse_data <- mouse_data %>%
  mutate(
    mutation = map_chr(
      full_text,
      find_pd_mutations
    )
  )
```

# 16. Alpha-Synuclein Related Models

```{r}
mouse_data <- mouse_data %>%
  mutate(
    alpha_synuclein_related = case_when(
      
      str_detect(
        full_text,
        regex(
          "alpha.?synuclein|α.?synuclein|Snca",
          ignore_case = TRUE
        )
      ) ~ "YES",
      
      TRUE ~ "NO"
    )
  )
```

# 17. GBA1 / Gaucher Related Models

```{r}
mouse_data <- mouse_data %>%
  mutate(
    gaucher_related = case_when(
      
      str_detect(
        full_text,
        regex(
          paste(
            "Gba1",
            "GCase",
            "glucocerebrosidase",
            "glucosylceramide",
            "glucosylsphingosine",
            "Gaucher",
            sep = "|"
          ),
          ignore_case = TRUE
        )
      ) ~ "YES",
      
      TRUE ~ "NO"
    )
  )
```

# 18. Classify Parkinson's Disease Model

```{r}
find_pd_model_type <- function(x) {
  
  if (is.na(x)) {
    
    return(
      NA_character_
    )
  }
  
  
  model_type <- character(0)
  
  
  ## GBA1
  
  if (str_detect(
    x,
    regex(
      "Gba1|GCase|glucocerebrosidase|Gaucher",
      ignore_case = TRUE
    )
  )) {
    
    model_type <- c(
      model_type,
      "GBA1 / Gaucher-associated model"
    )
  }
  
  
  ## alpha-synuclein
  
  if (str_detect(
    x,
    regex(
      "Snca|alpha.?synuclein|α.?synuclein",
      ignore_case = TRUE
    )
  )) {
    
    model_type <- c(
      model_type,
      "Alpha-synuclein model"
    )
  }
  
  
  ## LRRK2
  
  if (str_detect(
    x,
    regex(
      "Lrrk2",
      ignore_case = TRUE
    )
  )) {
    
    model_type <- c(
      model_type,
      "LRRK2 model"
    )
  }
  
  
  ## PINK1
  
  if (str_detect(
    x,
    regex(
      "Pink1",
      ignore_case = TRUE
    )
  )) {
    
    model_type <- c(
      model_type,
      "PINK1 model"
    )
  }
  
  
  ## Parkin
  
  if (str_detect(
    x,
    regex(
      "Prkn|Parkin",
      ignore_case = TRUE
    )
  )) {
    
    model_type <- c(
      model_type,
      "Parkin model"
    )
  }
  
  
  ## DJ-1
  
  if (str_detect(
    x,
    regex(
      "Park7|DJ.?1",
      ignore_case = TRUE
    )
  )) {
    
    model_type <- c(
      model_type,
      "DJ-1 model"
    )
  }
  
  
  ## VPS35
  
  if (str_detect(
    x,
    regex(
      "Vps35",
      ignore_case = TRUE
    )
  )) {
    
    model_type <- c(
      model_type,
      "VPS35 model"
    )
  }
  
  
  ## other model
  
  if (length(model_type) == 0) {
    
    return(
      "Other Parkinson-related model"
    )
  }
  
  
  paste(
    unique(model_type),
    collapse = "; "
  )
}
```

```{r}
mouse_data <- mouse_data %>%
  mutate(
    pd_model_type = map_chr(
      full_text,
      find_pd_model_type
    )
  )
```

# 19. Create Final Dataset

```{r}
pd_mouse_data <- mouse_data %>%
  select(
    stock_number,
    strain_name,
    gene,
    mutation,
    pd_model_type,
    alpha_synuclein_related,
    gaucher_related,
    genetic_background,
    common_uses,
    description,
    phenotype,
    development,
    breeding,
    jax_url,
    full_text
  ) %>%
  arrange(
    gene,
    stock_number
  )
```

# 20. Check Results

```{r}
cat(
  "\nTotal Parkinson's disease mouse strains:",
  nrow(pd_mouse_data),
  "\n"
)


pd_mouse_data %>%
  select(
    stock_number,
    strain_name,
    gene,
    mutation,
    pd_model_type
  )
```

```{r}
View(
  pd_mouse_data
)
```

# 21. GBA1 Mouse Models

```{r}
gba1_mice <- pd_mouse_data %>%
  filter(
    gaucher_related == "YES"
  )


gba1_mice %>%
  select(
    stock_number,
    strain_name,
    gene,
    mutation,
    genetic_background,
    common_uses,
    phenotype,
    jax_url
  )
```

# 22. Alpha-Synuclein Mouse Models

```{r}
snca_mice <- pd_mouse_data %>%
  filter(
    alpha_synuclein_related == "YES"
  )


snca_mice %>%
  select(
    stock_number,
    strain_name,
    gene,
    mutation,
    pd_model_type,
    jax_url
  )
```

# 23. Save Complete Dataset

```{r}
write_csv(
  pd_mouse_data,
  "JAX_Parkinson_Disease_Mice.csv"
)
```

# 24. Save Summary Dataset

```{r}
pd_mouse_summary <- pd_mouse_data %>%
  select(
    stock_number,
    strain_name,
    gene,
    mutation,
    pd_model_type,
    alpha_synuclein_related,
    gaucher_related,
    genetic_background,
    common_uses,
    jax_url
  )


write_csv(
  pd_mouse_summary,
  "JAX_Parkinson_Disease_Mice_Summary.csv"
)
```

# 25. Save GBA1 Models

```{r}
write_csv(
  gba1_mice,
  "JAX_GBA1_Parkinson_Mice.csv"
)
```

# 26. Final Summary

```{r}
cat(
  "\nExtraction completed.\n"
)

cat(
  "Total PD mouse strains:",
  nrow(pd_mouse_data),
  "\n"
)

cat(
  "GBA1 / Gaucher-related strains:",
  sum(pd_mouse_data$gaucher_related == "YES",
      na.rm = TRUE),
  "\n"
)

cat(
  "Alpha-synuclein-related strains:",
  sum(pd_mouse_data$alpha_synuclein_related == "YES",
      na.rm = TRUE),
  "\n"
)
```

# 27. Close Browser

```{r}
b$close()
```











